### 2018-12-12 chapters/1-introduction.tex
tildes

Prostate cancer (PCa) is the most common cancer in men, and the second most
common among the causes of death related to cancer. For example in USA, 161 360
new cases of PCa are estimated to be diagnosed in 2017, while the estimated
cancer related deaths are 26 730 \citep{Siegel2017}. However, in approximately
half of the cases of newly diagnosed PCa, the patients have a low risk of death
from the disease \citep{Walsh2007, Draisma2003}. Due to this wide range of
possible outcomes, it is important to accurately predict the risk caused by
PCa and to stratify patients accordingly aiming to limit over-treatment and
PCa mortality simultaneously.

@@

Various different fitting methods have been applied for modeling PCa DWI signal
decay. The biexponential function \citep{Mulkern2006} provides the best fitting
quality for DWI data sets acquired using ``high'' b values ($\sim$2000 s/mm²)
\citep{Jambor2015Evaluation}. However, it is not robust to noise and has low
repeatability. In contrast, the kurtosis function \citep{Jensen2005} provides
similar fitting quality while being substantially more robust to noise
\citep{Jambor2015Evaluation}. Texture features of parametric maps derived from
the kurtosis function have not been evaluated and hold promise by better signal
characterization compared with the most commonly used monoexponential function
\citep{Toivonen2015}. Other MRI methods, such as T₂-mapping (T₂) and anatomical
T₂-weighted imaging (T₂w), could provide complimentary information to DWI for
prediction of PCa characteristics \citep{Jambor2015Relaxation}.

@@

The current study is first of its kind in multiple aspects: a) direct comparison
of textures extracted from T₂w and T₂ relaxation maps, b) elevation of texture
features from non-monoexponetial DWI signal decay using high quality data sets,
and c) evaluation of a large number of texture extraction methods and parameters
to calculate them in a multi-dimensional high quality MRI data sets of patients
with PCa.

>>>>

Prostate cancer (PCa) is the most common cancer in men, and the second most
common among the causes of death related to cancer. For example in USA, 161~360
new cases of PCa are estimated to be diagnosed in 2017, while the estimated
cancer related deaths are 26~730 \citep{Siegel2017}. However, in approximately
half of the cases of newly diagnosed PCa, the patients have a low risk of death
from the disease \citep{Walsh2007, Draisma2003}. Due to this wide range of
possible outcomes, it is important to accurately predict the risk caused by
PCa and to stratify patients accordingly aiming to limit over-treatment and
PCa mortality simultaneously.

@@

Various different fitting methods have been applied for modeling PCa DWI signal
decay. The biexponential function \citep{Mulkern2006} provides the best fitting
quality for DWI data sets acquired using ``high'' b values ($\sim$2000~s/mm²)
\citep{Jambor2015Evaluation}. However, it is not robust to noise and has low
repeatability. In contrast, the kurtosis function \citep{Jensen2005} provides
similar fitting quality while being substantially more robust to noise
\citep{Jambor2015Evaluation}. Texture features of parametric maps derived from
the kurtosis function have not been evaluated and hold promise by better signal
characterization compared with the most commonly used monoexponential function
\citep{Toivonen2015}. Other MRI methods, such as T₂-mapping (T₂) and anatomical
T₂-weighted imaging (T₂w), could provide complimentary information to DWI for
prediction of PCa characteristics \citep{Jambor2015Relaxation}.

@@

The current study is first of its kind in multiple aspects: a)~direct comparison
of textures extracted from T₂w and T₂ relaxation maps, b)~elevation of texture
features from non-monoexponetial DWI signal decay using high quality data sets,
and c)~evaluation of a large number of texture extraction methods and parameters
to calculate them in a multi-dimensional high quality MRI data sets of patients
with PCa.
